\vspace{24pt} Comparison of Different Data Layouts for Columnar In-Memory Databases on the Basis of an Example Application

### 2018-08-31 paper/paper.tex
rewerite abstract to fit title

\maketitle
\begin{abstract}
The taxi business is an extremely competitive market. Private ridesharing companies such as Uber or Lynx have grown tremendously in the last decade. In order to survive as a traditional taxi company, the drivers have to increase their profit even further. Therefore, we created an application, that analyses taxi data recorded over one day in the city of Shenzhen. We examine which taxis were the most profitable ones by calculating the distances and times driven with a passenger. From this information, we can draw specific recommendations, where to take passengers at a certain time, so that the profit can be maximized.
\end{abstract}

>>>>

\maketitle
\begin{abstract}
With are more and more devices that are equipped with GPS and generate trajectory data analyzing and using this data catches attention increasingly. That is why besides using some specialized trajectory processing systems for that kind of data the interest in using common databases, especially columnar in-memmory systems, for this task rises. We compare three different data layouts for such databases based on a real-world usecase. Therefore we developed an example application with taxi data and benchmarked our those data layouts against typical queries of our usecase.
\end{abstract}
